\plaintitle

### 2025-05-21 docs/style/article-body.tex

\hypertarget{introduction}{%
\section{1 INTRODUCTION}\label{introduction}}

@@

\hypertarget{theory}{%
\subsection{2 THEORY}\label{theory}}

@@

\hypertarget{shot-noise-quantum-fluctuations}{%
\subsubsection{2.1 Shot noise quantum fluctuations}\label{shot-noise-quantum-fluctuations}}

@@

\hypertarget{background}{%
\subsection{3 BACKGROUND}\label{background}}

@@

\hypertarget{optical-rng-module}{%
\subsubsection{3.1 Optical RNG module}\label{optical-rng-module}}

@@

\hypertarget{adc-converter}{%
\subsubsection{3.2 ADC converter}\label{adc-converter}}

@@

\hypertarget{microcontroller}{%
\subsubsection{3.3 Microcontroller}\label{microcontroller}}

@@

\hypertarget{toeplitz-extraction}{%
\subsubsection{3.4 Toeplitz extraction}\label{toeplitz-extraction}}

@@

\hypertarget{summary}{%
\subsubsection{3.5 Summary}\label{summary}}

@@

\hypertarget{related-works}{%
\subsection{4 RELATED WORKS}\label{related-works}}

@@

\hypertarget{methodology}{%
\subsection{5 METHODOLOGY}\label{methodology}}

@@

\hypertarget{phase-one}{%
\subsubsection{5.1 Phase one}\label{phase-one}}

@@

\hypertarget{phase-two}{%
\subsubsection{5.2 Phase two}\label{phase-two}}

@@

\hypertarget{evaluation}{%
\subsubsection{5.3 Evaluation}\label{evaluation}}

@@

\hypertarget{limitations}{%
\subsubsection{5.4 Limitations}\label{limitations}}

@@

\hypertarget{results}{%
\subsection{6 RESULTS}\label{results}}

@@

\hypertarget{phase-one-1}{%
\subsubsection{6.1 Phase one}\label{phase-one-1}}

@@

\hypertarget{phase-two-1}{%
\subsubsection{6.2 Phase two}\label{phase-two-1}}

@@

\hypertarget{conclusion}{%
\subsection{7 CONCLUSION}\label{conclusion}}

\hypertarget{changelog}{%
\subsection{CHANGELOG}\label{changelog}}

>>>>

\section{1 INTRODUCTION}\label{introduction}

@@

\subsection{2 THEORY}\label{theory}

@@

\subsubsection{2.1 Shot noise quantum fluctuations}\label{shot-noise-quantum-fluctuations}

@@

\subsection{3 BACKGROUND}\label{background}

@@

\subsubsection{3.1 Optical RNG module}\label{optical-rng-module}

@@

\subsubsection{3.2 ADC converter}\label{adc-converter}

@@

\subsubsection{3.3 Microcontroller}\label{microcontroller}

@@

\subsubsection{3.4 Toeplitz extraction}\label{toeplitz-extraction}

@@

\subsubsection{3.5 Summary}\label{summary}

@@

\subsection{4 RELATED WORKS}\label{related-works}

@@

\subsection{5 METHODOLOGY}\label{methodology}

@@

\subsubsection{5.1 Phase one}\label{phase-one}

@@

\subsubsection{5.2 Phase two}\label{phase-two}

@@

\subsubsection{5.3 Evaluation}\label{evaluation}

@@

\subsubsection{5.4 Limitations}\label{limitations}

@@

\subsection{6 RESULTS}\label{results}

@@

\subsubsection{6.1 Phase one}\label{phase-one-1}

@@

\subsubsection{6.2 Phase two}\label{phase-two-1}

@@

\subsection{7 CONCLUSION}\label{conclusion}

Observing the results, we can place them into the context of the limits imposed by the ADC, as discussed in Section 3.2. In (3), we calculate the average execution speed required to be \(2.667 \mu\) for the ADC that requires soldering to the microcontroller. From Tables \ref{tab:iter5} and \ref{tab:iter6} we demonstrate execution speeds well below that, with iteration 5 as well as iteration 6 -- specifically with bitsets -- being the most prominent results to discuss. Here, our implementation achieved speeds of \(0.0501 \mu s\) and \(0.0474 \mu\) respectively which within the bounds of the ADC listed in Section 3.2. The built in ADC on Teensy has an effective sample rate of 1 MSPS (\emph{e.g. half of MAX11102AUB}), which would require an average execution speed of \textasciitilde{}\(2.667/2 \mu s \approx 1.334 \mu s\), making our implementation suitable even for that limited conversion speed.

The main culprit that led other iterations to not be viable was the inclusion of \texttt{std::vector}, which was used to ensure we could deliver variable lengths of our return data -- e.g.~either 32, 64 or 128 bits. The overhead introduced from initializing and populating the vector led to significant delays in execution speed, leading to all other attempts at optimization to be superfluous. In fact, any other complexities led to significantly worse results than the naive, original implementation.

However, it is important to note that both of these implementations has a hard limit of working on 64 bits input. Whereas larger bitstrings still yield results with high entropy, the execution speed increases far above the hardware limitations, as evident in \ref{tab:iter6}. Iteration 5 is hard capped at using only 64 bits input, as we need to store the bits in fixed-size integers before running them through the algorithm, and on embedded machines we have no larger integer types available.

One issue still remains concerning the size of the input string and subsequent output string. The larger the size of the matrix provided to the Toeplitz function (\emph{e.g.~the larger our input}), the higher the potential overall entropy becomes. As our implementation is essentially capped at 64 bits input at this point in time (\emph{without being limited by the hardware}), this may or may not prove to not be secure enough for use in real world applications. This, however, is out of scope for this particular thesis, but a consideration nonetheless.

\subsection{CHANGELOG}\label{changelog}
